---
title: "Assignment_2"
author: "Taewon"
date: '2021 10 2 '
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 2

This is the **assignment 2** for R programming class and includes the following items;

*1. Make a data frame from the air quality dataset*

*2. In the same chunk clean the dataset from NA values*

*3. Knit the RMarkdown file and make a PDF file*

*4. Save your RMarkdown and PDF files and commit them*

*5. Push the  RMarkdown and PDF files to the repository*

*6. Check your GitHub and your repository*

*7. Submit the link of your public repository to the i-class assignment 2*

### Assignment 2-1
```{r}
x <- data.frame(airquality)
x
```

### Assignment 2-2
- Method1  
```{r}
bad <- is.na(x)
bad
x1 <- x[!bad]
```
- Method2  
```{r}
good <- complete.cases(x)
good
x2 <- x[good, ]
x2
```
### Assignment 2-3
"Knit to PDF" function does not work due to the below reason which I don't understand  
'LaTeX failed to compile Rmarkdown_Assignment2.tex. See https://yihui.org/tinytex/r/#debugging for debugging tips. See Rmarkdown_Assignment2.log for more info.'
So I knit to Word file first and convert it to PDF.

### Assignment 2-4 to 2-7
I did as per the instruction. Thank you.

## END